Fixed-Parameter Tractable Sampling for RNA Design with Multiple Target Structures

### 2018-05-15 RNARedPrint-Bioinfo2018.tex
Update on Overleaf.

\begin{table}[t]
\centering
\medskip
\begin{tabular}{@{}>{\bf}l@{\quad}>{\tt}l@{\quad}@{\quad}c@{\quad}c@{\quad}c@{}}
             &   \textbf{\textrm{Dataset}}   & {\bfseries\ourprog{}} & \textbf{Uniform} & \textbf{Improvement} \\\toprule
  Seeds      & 2str & 21.69 ($\pm$4.37) & 37.74 ($\pm$6.45) & 74\%\\
             & 3str & 18.10 ($\pm$3.98) & 30.49 ($\pm$5.41) & 71\%\\
             & 4str & 20.15 ($\pm$3.83) & 32.32 ($\pm$5.23) & 62\%\\
             & PK60 & 12.12 ($\pm$3.04) & 19.81 ($\pm$4.24) & 68\%\\
             & PK80 & 13.81 ($\pm$3.63) & 24.05 ($\pm$4.93) & 82\%\\
             & LE80 & 10.54 ($\pm$2.77) & 17.80 ($\pm$4.17) & 78\%\\
             \midrule

  Optimized  & 2str & 5.42 ($\pm$1.27) & 7.95 ($\pm$1.75) & 35\%\\
             & 3str & 5.10 ($\pm$1.10) & 7.04 ($\pm$1.52) & 31\%\\
             & 4str & 9.17($\pm$1.51) & 13.25 ($\pm$2.13) & 38\% \\
             & PK60 & 3.75 ($\pm$1.19) & 6.45 ($\pm$1.84) & 125\%\\
             & PK80 & 3.52 ($\pm$1.58) & 7.99 ($\pm$2.35) & 107\%\\
             & LE80 & 3.59 ($\pm$1.11) & 5.88 ($\pm$1.59) & 215\%\\
             \bottomrule
\end{tabular}\\[1em]

\caption{Comparison of the multi-stable design objective function (
  Eq.~(\ref{eq:blueprintobjective}) of sequences sampled by \ourprog{}
  vs.\ uniform samples for three benchmark sets; before (seeds) and
  after optimization (optimized). We report the average scores with
  standard deviations. Smaller scores are better; the final column
  reports our improvements over uniform sampling.}
\label{tab:benchmark-results}
\end{table}

>>>>

\begin{table}[t]
\centering
\medskip
\begin{tabular}{@{}>{\bf}l@{\quad}>{\tt}l@{\quad}@{\quad}c@{\quad}c@{\quad}c@{}}
             &   \textbf{\textrm{Dataset}}   & {\bfseries\ourprog{}} & \textbf{Uniform} & \textbf{Improvement} \\\toprule
  Seeds      & 2str & 21.69 ($\pm$4.37) & 37.74 ($\pm$6.45) & 74\%\\
             & 3str & 18.10 ($\pm$3.98) & 30.49 ($\pm$5.41) & 71\%\\
             & 4str & 20.15 ($\pm$3.83) & 32.32 ($\pm$5.23) & 62\%\\
             \midrule
             & PK60 & 12.12 ($\pm$3.04) & 19.81 ($\pm$4.24) & 68\%\\
             & PK80 & 13.81 ($\pm$3.63) & 24.05 ($\pm$4.93) & 82\%\\
             & LE80 & 10.54 ($\pm$2.77) & 17.80 ($\pm$4.17) & 78\%\\
             \midrule

  Optimized  & 2str & 5.42 ($\pm$1.27) & 7.95 ($\pm$1.75) & 35\%\\
             & 3str & 5.10 ($\pm$1.10) & 7.04 ($\pm$1.52) & 31\%\\
             & 4str & 9.17($\pm$1.51) & 13.25 ($\pm$2.13) & 38\% \\
             \midrule
             & PK60* & 3.75 ($\pm$1.19) & 6.45 ($\pm$1.84) & 125\%\\
             & PK80* & 3.52 ($\pm$1.58) & 7.99 ($\pm$2.35) & 107\%\\
             & LE80* & 3.59 ($\pm$1.11) & 5.88 ($\pm$1.59) & 215\%\\
             \bottomrule
\end{tabular}\\[1em]

\caption{Comparison of the multi-stable design objective function (
  Eq.~(\ref{eq:blueprintobjective}) of sequences sampled by \ourprog{}
  vs.\ uniform samples for three benchmark sets; before (seeds) and
  after optimization (optimized). We report the average scores with
  standard deviations. Smaller scores are better; the final column
  reports the mean of our improvements over uniform sampling. \TODO{PK datasets ensemble free energy was not available thus approximated with mfe energy. Mention negative scores somewhere! Asterisk benchmarks are not complete yet.}}
\label{tab:benchmark-results}
\end{table}
